Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-09 csf-2017/paper.tex
Start on section about stack and return pointer management discipline.

Explain our model of linking

\section{Stack and return pointer management using local capabilities}
\begin{itemize}
\item Issues to consider:
\begin{itemize}
\item no global store-local capabilities
\item clearing the stack
\item clearing (some) registers
\item constructing return pointers
\item constructing callbacks
\item invoking the adversary's callbacks
\end{itemize}
\item Reusable macro-instructions for stack and return pointer management
\begin{itemize}
\item taking care of the stuff above
\end{itemize}
\end{itemize}

>>>>

% Contrary to more traditional assembly languages, capability machines do not
% allow literal addresses to appear as part of instructions. This means that we

Explain our model of linking
\dominique{not sure what we want to say about it here...}

\section{Stack and return pointer management using local capabilities}

One of the contributions in this paper is a demonstration that local
capabilities on a capability machine can be used in a stack and return pointer
management scheme that enforces control flow integrity in a way that is provably
watertight, potentially efficient, does not rely on a trusted central stack
manager, and with support for exposing higher-order interfaces to an adversary.
In this section, we explain this discipline. We start by explaining the
high-level approach, the different issues that need to be taken into account,
starting with first-order interfaces and moving onto a higher-order setting
after that. After that, we define a number of reusable macro-instructions that
can be used to conveniently apply the proposed discipline in subsequent
examples.

The basic idea of our approach is actually rather simple: we stick to a single,
rather standard C stack and register-passed return pointers in much the same way
as a standard C ABI. However, to prevent various ways of misusing this basic
scheme, we put local capabilities to work and need to perform a number of
not-always-obvious checks and safety measures.

\paragraph{Invoking the adversary}
* stack and return pointer as local caps
* clearing registers
* clearing the stack

\paragraph{Returning from the adversary}
* return pointer as enter pointer to activation record on the stack.
* activation record contains previous pc and stack pointer

\paragraph{Invoking an adversary callback}
* must be global

\paragraph{Having a callback invoked by the adversary}
* checking the received stack pointer

\begin{itemize}
\item Issues to consider:
\begin{itemize}
\item no global store-local capabilities
\item clearing the stack
\item clearing (some) registers
\item constructing return pointers
\item constructing callbacks
\item invoking the adversary's callbacks
\end{itemize}
\item Reusable macro-instructions for stack and return pointer management
\begin{itemize}
\item taking care of the stuff above
\end{itemize}
\end{itemize}
